Farley et al. 2024 B

### 2025-01-13 IndividualStudies/SF_2024_B.qmd
Minor updates, new help symbol

@@

## Displays the reactive dataframe
datatable(SF_2024_data_reactive, options = list(pageLength = 25))

>>>>

## Study details

### Lipid probes utilized

### Cell line analyzed

### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>

@@

## Displays the reactive dataframe
datatable(SF_2024_data_reactive, options = list(pageLength = 20))
